Replication Script to JSS Submission

### 2016-05-21 JSS/submission/replicationScript.Rnw
updated statGeneal.rda

\documentclass{article}
\parindent 0pt
\title{Replication Script to JSS Submission}
\begin{document}

\author{Lindsay Rutter, Susan VanderPlas, Dianne Cook, Michelle A. Graham}
\date{\today}
\maketitle
\SweaveOpts{concordance=TRUE}
\tableofcontents

@@

<<>>=
rm(list=)
library("ggenealogy")
data("sbGeneal")
str(sbGeneal)
@

@@

<<>>=
data("statGeneal")
dim(statGeneal)
colnames(statGeneal)
@

@@

<<>>=
sbIG <- dfToIG(sbGeneal)
sbIG
@

@@

<<>>=
getBasicStatistics(sbIG)
@

@@

<<>>=
pathTN <- getPath("Tokyo", "Narow", sbIG, sbGeneal)
pathTN
@

@@

<<>>=
plotPath(pathTN)
@

@@

<<>>=
getYear("Bedford", sbGeneal)
getYear("Zane", sbGeneal)
@

@@

<<>>=
pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
plotPath(pathBZ, fontFace = 2)
@

@@

<<>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
@

@@

<<>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
@

@@

<<>>=
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<>>=
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
@

@@

<<>>=
library("dplyr")
indVec <- getNodes(statGeneal)
indVec <- indVec[which(indVec != "", )]
dFunc <- function(var) nrow(getDescendants(var, statGeneal, gen = 100))
numDesc <- sapply(indVec, dFunc)
table(numDesc)
which(numDesc == 159)
@

@@

<<>>=
plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<>>=
length(getChild("Peter Bloomfield", statGeneal))
nrow(getDescendants("Peter Bloomfield", statGeneal, gen = 100))
@

@@

<<>>=
statIG <- dfToIG(statGeneal)
@

@@

<<>>=
pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
@

>>>>

\documentclass{article}
\usepackage{float, hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{pgffor}

\title{Replication Script to JSS Submission}
\begin{document}

<<options, echo=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

\author{Lindsay Rutter, Susan VanderPlas, Dianne Cook, Michelle A. Graham}
\date{\today}
\maketitle
\SweaveOpts{concordance=TRUE}

@@

<<eval=TRUE>>=
rm(list=)
library("devtools")
load_all("ggenealogy")
library("ggenealogy")
data("sbGeneal")
str(sbGeneal)
@

@@

<<eval=TRUE>>=
data("statGeneal")
dim(statGeneal)
colnames(statGeneal)
@

@@

<<eval=TRUE>>=
sbIG <- dfToIG(sbGeneal)
sbIG
@

@@

<<eval=TRUE>>=
getBasicStatistics(sbIG)
@

@@

<<eval=TRUE>>=
pathTN <- getPath("Tokyo", "Narow", sbIG, sbGeneal)
pathTN
@

@@

<<eval=TRUE>>=
plotPath(pathTN)
@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPath(pathTN)
@
\end{figure}

@@

<<eval=TRUE>>=
getYear("Bedford", sbGeneal)
getYear("Zane", sbGeneal)
@

@@

<<eval=TRUE>>=
pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
plotPath(pathBZ, fontFace = 2)
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
@

@@

<<eval=TRUE>>=
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
@

@@

<<eval=TRUE>>=
library("dplyr")
indVec <- getNodes(statGeneal)
indVec <- indVec[which(indVec != "", )]
dFunc <- function(var) nrow(getDescendants(var, statGeneal, gen = 100))
numDesc <- sapply(indVec, dFunc)
table(numDesc)
which(numDesc == 159)
@

@@

<<eval=TRUE>>=
plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
length(getChild("Peter Bloomfield", statGeneal))
nrow(getDescendants("Peter Bloomfield", statGeneal, gen = 100))
@

@@

<<eval=TRUE>>=
statIG <- dfToIG(statGeneal)
@

@@

<<eval=TRUE>>=
pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
@

### 2016-05-21 JSS/submission/replicationScript.tex
updated statGeneal.rda

\title{Replication Script to JSS Submission}
\begin{document}

<<options, echo=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

\author{Lindsay Rutter, Susan VanderPlas, Dianne Cook, Michelle A. Graham}
\date{\today}
\maketitle
\SweaveOpts{concordance=TRUE}

@@

<<eval=TRUE>>=
rm(list=)
library("devtools")
load_all("ggenealogy")
library("ggenealogy")
data("sbGeneal")
str(sbGeneal)
@

@@

<<eval=TRUE>>=
data("statGeneal")
dim(statGeneal)
colnames(statGeneal)
@

@@

<<eval=TRUE>>=
sbIG <- dfToIG(sbGeneal)
sbIG
@

@@

<<eval=TRUE>>=
getBasicStatistics(sbIG)
@

@@

<<eval=TRUE>>=
pathTN <- getPath("Tokyo", "Narow", sbIG, sbGeneal)
pathTN
@

@@

<<eval=TRUE>>=
plotPath(pathTN)
@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPath(pathTN)
@
\end{figure}

@@

<<eval=TRUE>>=
getYear("Bedford", sbGeneal)
getYear("Zane", sbGeneal)
@

@@

<<eval=TRUE>>=
pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
plotPath(pathBZ, fontFace = 2)
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
@

@@

<<eval=TRUE>>=
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
@

@@

<<eval=TRUE>>=
library("dplyr")
indVec <- getNodes(statGeneal)
indVec <- indVec[which(indVec != "", )]
dFunc <- function(var) nrow(getDescendants(var, statGeneal, gen = 100))
numDesc <- sapply(indVec, dFunc)
table(numDesc)
which(numDesc == 159)
@

@@

<<eval=TRUE>>=
plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
length(getChild("Peter Bloomfield", statGeneal))
nrow(getDescendants("Peter Bloomfield", statGeneal, gen = 100))
@

@@

<<eval=TRUE>>=
statIG <- dfToIG(statGeneal)
@

@@

<<eval=TRUE>>=
pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
@

>>>>

\title{Replication Script to JSS Submission}
\usepackage{Sweave}
\begin{document}

\author{Lindsay Rutter, Susan VanderPlas, Dianne Cook, Michelle A. Graham}
\date{\today}
\maketitle
\input{replicationScript-concordance}

@@

\begin{Schunk}
\begin{Sinput}
> rm(list=)
> library("devtools")
> load_all("ggenealogy")
> library("ggenealogy")
> data("sbGeneal")
> str(sbGeneal)
\end{Sinput}
\begin{Soutput}
'data.frame':	390 obs. of  5 variables:
 $ child       : chr  "5601T" "Adams" "A.K." "A.K. (Harrow)" ...
 $ year        : num  1981 1948 1910 1912 1968 ...
 $ yield       : int  NA 2734 NA 2665 NA 2981 2887 2817 NA NA ...
 $ year.imputed: logi  TRUE FALSE TRUE FALSE FALSE FALSE ...
 $ parent      : chr  "Hutcheson" "Dunfield" NA "A.K." ...
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> data("statGeneal")
> dim(statGeneal)
\end{Sinput}
\begin{Soutput}
[1] 8165    6
\end{Soutput}
\begin{Sinput}
> colnames(statGeneal)
\end{Sinput}
\begin{Soutput}
[1] "child"   "parent"  "year"    "country" "school"  "thesis" 
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> sbIG <- dfToIG(sbGeneal)
> sbIG
\end{Sinput}
\begin{Soutput}
IGRAPH UNW- 230 340 -- 
+ attr: name (v/c), weight (e/n)
+ edges (vertex names):
 [1] 5601T    --Hutcheson        Adams    --Dunfield        
 [3] A.K.     --A.K. (Harrow)    Altona   --Flambeau        
 [5] Amcor    --Amsoy 71         Adams    --Amsoy           
 [7] Amsoy 71 --C1253            Anderson --Lincoln         
 [9] Bay      --York             Bedford  --Forrest         
[11] Beeson   --Kent             Blackhawk--Richland        
[13] Bonus    --C1266R           Bradley  --J74-39          
[15] Bragg    --Jackson          Bragg    --Bragg x D60-7965
+ ... omitted several edges
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> getBasicStatistics(sbIG)
\end{Sinput}
\begin{Soutput}
$isConnected
[1] FALSE

$numComponents
[1] 11

$avePathLength
[1] 5.333746

$graphDiameter
[1] 13

$numNodes
[1] 230

$numEdges
[1] 340

$logN
[1] 5.438079
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> pathTN <- getPath("Tokyo", "Narow", sbIG, sbGeneal)
> pathTN
\end{Sinput}
\begin{Soutput}
$pathVertices
[1] "Tokyo"    "Volstate" "Jackson"  "R66-873"  "Narow"

$yearVertices
[1] "1907"   "1942"   "1954.5" "1971.5" "1985"  
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPath(pathTN)
\end{Sinput}
\end{Schunk}

\begin{figure}[H]
\centering
\begin{Schunk}
\begin{Sinput}
> plotPath(pathTN)
\end{Sinput}
\end{Schunk}
\includegraphics{replicationScript-008}
\end{figure}

@@

\begin{Schunk}
\begin{Sinput}
> getYear("Bedford", sbGeneal)
\end{Sinput}
\begin{Soutput}
[1] 1978
\end{Soutput}
\begin{Sinput}
> getYear("Zane", sbGeneal)
\end{Sinput}
\begin{Soutput}
[1] 1985
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
> plotPath(pathBZ, fontFace = 2)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
> plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library("dplyr")
> indVec <- getNodes(statGeneal)
> indVec <- indVec[which(indVec != "", )]
> dFunc <- function(var) nrow(getDescendants(var, statGeneal, gen = 100))
> numDesc <- sapply(indVec, dFunc)
> table(numDesc)
\end{Sinput}
\begin{Soutput}
numDesc
   0    1    2    3    4    5    6    7    8    9   10   11   12   13   14   15 
6251  322  145   88   58   36   31   22   23   14   17   13   14   10    9    6 
  16   17   18   19   20   21   22   23   24   25   26   27   29   30   34   37 
   4    3    2    5    7    4    3    3    2    2    6    1    1    3    2    1 
  38   40   41   44   45   48   49   60   61   75   77   84  159 
   1    1    1    1    1    1    2    1    1    1    1    1    1 
\end{Soutput}
\begin{Sinput}
> which(numDesc == 159)
\end{Sinput}
\begin{Soutput}
David Cox 
     1980 
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> length(getChild("Peter Bloomfield", statGeneal))
\end{Sinput}
\begin{Soutput}
[1] 26
\end{Soutput}
\begin{Sinput}
> nrow(getDescendants("Peter Bloomfield", statGeneal, gen = 100))
\end{Sinput}
\begin{Soutput}
[1] 49
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> statIG <- dfToIG(statGeneal)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
> plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
\end{Sinput}
\end{Schunk}
